Hydra Battles and Cie

### 2021-08-30 doc/hydras.tex
[latex] Prevent line breaks within syntactic units in code
https://github.com/coq-community/hydra-battles/issues/70#issue-980536040
[doc] Add an \inputsnippets command and demo it in Schutte/AP.v
update list of contributors

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, \thanks{With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury and Théo Zimmermann. The formalization of primitive recursive functions was originally authored by 
Russel O'Connor\cite{OConnor05}.}}
\date{\today}
%\date{August 2021}

>>>>

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, \thanks{With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Clément Pit-Claudel, and Théo Zimmermann. The formalization of primitive recursive functions was originally authored by 
Russel O'Connor\cite{OConnor05}.}}
\date{\today}
%\date{August 2021}
